Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-11-18 doc/JFLA2022/paper.tex
attempt at explaining why we use coq_makefile

\newcommand{\TODO}[2][]{[\textcolor{red}{TODO (#1):} \emph{#2}]}
\newcommand{\coq}{Coq\xspace}
\newcommand{\coqdoc}{Coqdoc\xspace}
\newcommand{\coqmakefile}{coq\_makefile\xspace}
\newcommand{\community}{Coq-community\xspace}
\newcommand{\gaia}{Gaia\xspace}
\newcommand{\alectr}{Alectryon\xspace}
\newcommand{\equations}{Equations\xspace}
\newcommand{\Hydras}{Hydras \& Co$\text.$\xspace}
%\newcommand{\Hydras}{Hydra-battles\xspace}

@@

In practice, we do still support building the whole project with \coqmakefile, and we actually rely on this build system in our documentation generation pipeline.

>>>>

\newcommand{\TODO}[2][]{[\textcolor{red}{TODO (#1):} \emph{#2}]}
\newcommand{\coq}{Coq\xspace}
\newcommand{\coqdoc}{Coqdoc\xspace}
\newcommand{\coqmakefile}{coq\_makefile\xspace}
\newcommand{\community}{Coq-community\xspace}
\newcommand{\gaia}{Gaia\xspace}
\newcommand{\alectr}{Alectryon\xspace}
\newcommand{\equations}{Equations\xspace}
\newcommand{\Hydras}{Hydras \& Co$\text.$\xspace}
\newcommand{\make}{\texttt{make}\xspace}
%\newcommand{\Hydras}{Hydra-battles\xspace}

@@

In practice, we still support building the whole project using \make via the \coqmakefile tool bundled with \coq, and we actually rely on this build system in our documentation generation pipeline. The main reason is that using \coqmakefile is currently more convenient than Dune for local IDE-based Coq code development, e.g., due to Dune placing generated files in a separate directory. We expect to migrate fully to Dune in the near future.
